### 2013-07-24 doc/asplos14/evaluation.tex
eval uts

We look at two classes of trees, T1 and T3, from
the original benchmark. T1 trees are very shallow and wide (i.e., significant
parallel slack), while T3 trees are very deep (i.e., little parallel slack).
When the access to each vertex is a random access, the critical path to search
T3 trees is very long, hence the low performance and scalability. On such
trees, we do not expect there to be sufficient concurrency for any system,
including \Grappa, to achieve high throughput -- at the 16-node data point,
the average active tasks per core over the search is 775 for T1 and
only 13 for T3.
On the other hand, \Grappa performs and scales very well for T1
trees.

@@

\begin{table}[htb]
\small
\begin{center}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                               &   GUPS            &   BFS   & IntSort & UTS & Pagerank \\ \hline
App. message rate/core (K/s)  & 984            &  983   &      &     \\
%Application message bytes     & 31.8 $\pm$ 1.2    & \\
Avg. App. message bytes & 31.8              & 33.9    &      & \\
Network BW per node (MB/s)    & 478           & 511 &    &      \\
%Network message bytes         & 23.2K $\pm$ 12.4K & \\ \hline
Avg. Network message bytes     & 23.2K             & 4.3K    & &    \\ \hline
Avg. active tasks/core         & 0.9               & 58.2    &  &  \\
Max. active tasks/core         & 1                 & 128     &  &   \\
Avg. ready queue length/core   & 2.3               & 6.1     &  &    \\
Avg. Ctx switch rate/core (K/s) & 34.2           & 539  &     &  \\ 
Steal count                    & 0                 & 0       &  &     \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table}

>>>>

We look at two classes of trees, T1 and T3, from
the original benchmark. T1 trees are very shallow and wide (i.e., significant
parallel slack \cite{Valiant:1990}), while T3 trees are very deep (i.e., little parallel slack).
Given that access to each vertex is a random access, the critical path to search
T3 trees is very long, hence the low performance and scalability. On such
trees, we do not expect there to be sufficient concurrency for any system,
including \Grappa, to achieve high throughput -- at the 16-node data point,
the average active tasks per core over the search is 775 for T1 and
only 13 for T3. Given the lack of parallelism, scaling up only serves
to reduce throughput by distributing the tree to more machines.
On the other hand, \Grappa performs and scales very well for T1
trees.

We compared this to a in-memory modification of the UPC implementation
of UTS \cite{UTS}, where each core hosts a UPC ``THREAD''. Berkeley
UPC (BUPC) is built upon GASNet, like Grappa, but it uses RDMA transfers directly
and the compiler overlaps remote communication when possible. We expect BUPC to
perform similarly on the T3 tree, where there is little parallelism to
overlap communication and computation, and no better than T3 on T1,
given the inability to overlap vertices on each core without
multithreading (a multithreaded variant of UPC has been evaluated in
\cite{HotSLAW}). Our experiments confirm that BUPC achieves the lower throughput of
Grappa on T3 for \emph{both} the T1 and T3 trees.

@@

\begin{table*}[htb]
\begin{center}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                               &   GUPS            &   BFS   & IntSort & UTS & Pagerank \\ \hline
Application message rate/core  & 984K/s            &  983K   &           \\
%Application message bytes     & 31.8 $\pm$ 1.2    & \\
Avg. Application message bytes & 31.8              & 33.9    &       \\
Network bandwidth per node     & 478MB/s           & 511MB/s &          \\
%Network message bytes         & 23.2K $\pm$ 12.4K & \\ \hline
Avg. Network message bytes     & 23.2K             & 4.3K    &     \\ \hline
Avg. active tasks/core         & 0.9               & 58.2    &    \\
Max. active tasks/core         & 1                 & 128     &     \\
Avg. ready queue length/core   & 2.3               & 6.1     &      \\
Avg. Context switch rate/core & 34.2K/s           & 539K/s  &       \\ 
Steal count                    & 0                 & 0       &       \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table*}
